Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-15 paper/main.tex
\autoref \o/

As stated in Section \ref{sec:lengthextension}, none of the \ac{SHA}-3
candidates are vulnerable to the length-extension attack. Since we are
interested in finding out how Tahoe-\ac{LAFS} performs when utilizing the
\ac{SHA}-3 functions, we can remove the lines that fixes the length-extension
problems manually. In addition, to try out one of the new implementations, we
change line one in Listing \ref{lst:hashutil}, and an example of this can be
seen in Listing \ref{lst:hashutilmod}.

@@

For the same reasons, some of the built-in unit tests of Tahoe-LAFS fail when
changing this line, because they contain test fixtures made with the included
SHA-256.  An implication of this is that uploading of mutable files renders
impossible, since the internal verification fails. For this reason, \emph{only
immutable files} are tested and measured in this paper. Implications of this are
further discussed in Chapter \ref{ch:discussion}.

@@

As stated in Section \ref{sec:modtahoe}, only immutable files are tested. The
mutable files are not tested because of our way of integrating the SHA-3
candidates within the Tahoe-LAFS code.

@@

Listing \ref{lst:hashutil_time} demonstrates the use of the {\verb time } module
in Python. On every call to {\verb update() } or {\verb digest() }, a variable
is increased with the time it took to run the underlying hash library
functionality. Similarly, Listing \ref{lst:testrunner} shows the use of the
{\verb date } command to calculate the number of seconds it takes it takes for
Tahoe to put a file to the grid.

@@

\section{SUPERCOP benchmarks}
\label{sec:results:supercop}
The results of the \ac{SHA}-3 256-bit functions and \ac{SHA}-256 benchmarking in
\ac{SUPERCOP} can be seen in tables \ref{tbl:supercop:long},
\ref{tbl:supercop:4096}, \ref{tbl:supercop:1536}, \ref{tbl:supercop:576},
\ref{tbl:supercop:64} and \ref{tbl:supercop:8}. The lower the numbers, the
faster and better the algorithms performed in the test.

@@

\subsection{Theoretical optimized results}
We have not use the fastest available implementations for all of the
candidates, we also know that our bindings creates an overhead for all calls.
Therefore we have tried to calculate the results that could have been achieved
in Tahoe-\ac{LAFS} if we had managed to obtain the speeds of the fastest
implementations in \{SUPERCOP}. The results can be seen in appendix
\ref{appendix:optimzed_sha3}.

@@

Tables \ref{tbl:tahoe:optimized_g} and \ref{tbl:tahoe:optimized_p} exhibit
results calculated which theoretically could have been achieved using the best
\ac{SUPERCOP} implementation for each candidate in Tahoe-\ac{LAFS}. The
calculations uses medians from Section \ref{sec:results:supercop} for the speed
of each candidate, the exact sizes for each call to the hash function from
Section \ref{sec:results:tahoedata}, and interpolation to estimate the time to
hash a length not recorded by \ac{SUPERCOP}. For lengths above 4096B, the
numbers for long data lengths are used. The results also assume only one core
of the reference processor (2,833 GHz) is used. We can see that some of the calculations,
e.g. for Shavite3 are worse than the result we achieved in our measurements,
this is probably due to interpollation being an inaccurate method to use for
the shorter lengths of data.

@@

% Use ordinary \chapters from here on..

>>>>

As stated in \autoref{sec:lengthextension}, none of the \ac{SHA}-3
candidates are vulnerable to the length-extension attack. Since we are
interested in finding out how Tahoe-\ac{LAFS} performs when utilizing the
\ac{SHA}-3 functions, we can remove the lines that fixes the length-extension
problems manually. In addition, to try out one of the new implementations, we
change line one in Listing \ref{lst:hashutil}, and an example of this can be
seen in Listing \ref{lst:hashutilmod}.

@@

For the same reasons, some of the built-in unit tests of Tahoe-LAFS fail when
changing this line, because they contain test fixtures made with the included
SHA-256.  An implication of this is that uploading of mutable files renders
impossible, since the internal verification fails. For this reason, \emph{only
immutable files} are tested and measured in this paper. Implications of this are
further discussed in \autoref{ch:discussion}.

@@

As stated in \autoref{sec:modtahoe}, only the Tahoe-\ac{LAFS} file type
\emph{immutable files} are tested. The mutable files are not tested because of
our way of integrating the SHA-3 candidates within the Tahoe-LAFS code.

@@

Listing \ref{lst:hashutil_time} demonstrates the use of the {\verb time } module
in Python. On every call to {\verb update() } or {\verb digest() }, a variable
is increased with the time it took to run the underlying hash library
functionality. Similarly, Listing \ref{lst:testrunner} shows the use of the
{\verb date } command in Bash to calculate the number of seconds it takes for
Tahoe to put a file to the grid.

@@

\section{SUPERCOP benchmarks}
The results of the \ac{SHA}-3 256-bit functions and \ac{SHA}-256 benchmarking in
\ac{SUPERCOP} can be found in \autoref{app:supercop:bench}.

@@

\subsection{Theoretical optimized results}
We have not use the fastest available implementations for all of the
candidates, we also know that our bindings creates an overhead for all calls.
Therefore we have tried to calculate the results that could have been achieved
in Tahoe-\ac{LAFS} if we had managed to obtain the speeds of the fastest
implementations in \ac{SUPERCOP}. The results can be seen in appendix
\ref{appendix:optimzed_sha3}.

@@

Tables \ref{tbl:tahoe:optimized_g} and \ref{tbl:tahoe:optimized_p} exhibit
results calculated which theoretically could have been achieved using the best
\ac{SUPERCOP} implementation for each candidate in Tahoe-\ac{LAFS}. The
calculations uses medians from \autoref{app:supercop:bench} for the speed
of each candidate, the exact sizes for each call to the hash function from
\autoref{sec:results:tahoedata}, and interpolation to estimate the time to
hash a length not recorded by \ac{SUPERCOP}. For lengths above 4096B, the
numbers for long data lengths are used. The results also assume only one core
of the reference processor (2,833 GHz) is used. We can see that some of the calculations,
e.g. for Shavite3 are worse than the result we achieved in our measurements,
this is probably due to interpolation being an inaccurate method to use for
the shorter lengths of data.

@@

\chapter{Results from SUPERCOP benchmark}
\label{app:supercop:bench}

Tables \ref{tbl:supercop:long}, \ref{tbl:supercop:4096},
\ref{tbl:supercop:1536}, \ref{tbl:supercop:576}, \ref{tbl:supercop:64} and
\ref{tbl:supercop:8} exhibits the results of the \ac{SHA}-3 256-bit functions
and \ac{SHA}-256 benchmarking in \ac{SUPERCOP}. The lower the numbers, the
faster and better the algorithms performed in the test.
